VIP-193: Committee-Based POA

### 2020-03-03 article.tex

After receiving $d$ valid endorsements, leader~$l_r$ needs to prepare and broadcast the header of the new block. A block header~$h_r$ must contain the following information:
\begin{itemize}
    \item Parent header reference 
    \item Round number, $r$
    \item Merkle tree root of the tx set, $\rho\left(\Sigma_r\right)$
    \item Leader's signature on the block summary, ${\tt Sig}_{\,l_r}(s_r)$
    \item VRF proofs of the committee membership from $d$ nodes, $\left\{\pi_{u_i,r}\right\}_{i=1}^d$
    \item Endorsement signatures from the same $d$ nodes, $\left\{{\tt SIG}_{u_i}(\bar{e}_{u,r})\right\}_{i=1}^d$
    \item For any $1\leq i<j\leq N$, $u_i$'s public key for verifying $\pi_{u_i,r}$ should be strictly smaller than that of $u_j$
    \item Leader's signature, ${\tt Sig}_{\,l_r}(\bar{h}_r)$ where $\bar{h}_r$ represents the header without a signature
    % \item Committee member list $\left(u_1<u_2<\dots<u_d\right)$
    % \item Merkle tree root of VRF proofs $\left\{\pi_{u_i,r}\right\}_{i=1}^d$
    % \item Merkle tree root of signatures $\left\{{\tt SIG}_{u_i}(\tau_r)\right\}_{i=1}^d$
    % \item Signature ${\tt Sig}_{\,l_r}(\Gamma_r)$
    % \item Other necessary header elements such as the state root, receipt root, gas limit and etc.
\end{itemize}

@@

\begin{algorithm}[H]
\caption{Procedure for validating the header of the new block generated in round $r$.}
\label{alg:header-valid}
\begin{spacing}{1.2}
\begin{algorithmic}[1]
    \vspace{1ex}
    \State Verify ${\tt Sig}_{\,l_r}(\bar{h}_r)$
    \State Verify that $r$ is the current round
    \State Verify that $l_r$ is the round leader
    \State Reconstruct and verify $s_r$ by Algorithm~\ref{alg:bs-valid}
    % \State Verify $\rho\left(\Sigma_r\right)$
    \For{$i=1,2,\dots,d$}
        \If{$i>1$}
            \State Verify that $u_i$'s public key for verifying $\pi_{u_i,r}$ is larger than that of $u_{i-1}$
        \EndIf
        \State Reconstruct and Verify $e_{u_i,r}$ by Algorithm~\ref{alg:endorse-valid}
    \EndFor
    % \State Construct $\Gamma_r$ and verify ${\tt Sig}_{\,l_r}(\Gamma_r)$
    % \State Construct header body~$\Omega$ and verify ${\tt Sig}_{\,l_r}(\Omega)$
    % \State Verify $\Sigma_r$ 
\end{algorithmic}
\end{spacing}
\end{algorithm}

>>>>

After receiving $d$ valid endorsements, leader~$l_r$ needs to prepare and broadcast the header of the new block. A block header~$h_r$ must contain the following information:
\begin{itemize}
    \item Parent header reference 
    \item Round number, $r$
    \item Merkle tree root of the tx set, $\rho\left(\Sigma_r\right)$
    \item Leader's signature on the block summary, ${\tt Sig}_{\,l_r}(s_r)$
    \item VRF proofs of the committee membership from $d$ nodes, $\left\{\pi_{u_i,r}\right\}_{i=1}^d$
    \item Endorsement signatures from the same $d$ nodes, $\left\{{\tt SIG}_{u_i}(\bar{e}_{u,r})\right\}_{i=1}^d$
    \item $\forall\,1\leq i<j\leq N$, $\pi_{u_i,r}<\pi_{u,j}$. It is made to reduce the number of combinations $l_r$ can try when arranging the vrf proofs.
    \item Leader's signature, ${\tt Sig}_{\,l_r}(\bar{h}_r)$ where $\bar{h}_r$ represents the header without a signature
    % \item Committee member list $\left(u_1<u_2<\dots<u_d\right)$
    % \item Merkle tree root of VRF proofs $\left\{\pi_{u_i,r}\right\}_{i=1}^d$
    % \item Merkle tree root of signatures $\left\{{\tt SIG}_{u_i}(\tau_r)\right\}_{i=1}^d$
    % \item Signature ${\tt Sig}_{\,l_r}(\Gamma_r)$
    % \item Other necessary header elements such as the state root, receipt root, gas limit and etc.
\end{itemize}

@@

\begin{algorithm}[H]
\caption{Procedure for validating the header of the new block generated in round $r$.}
\label{alg:header-valid}
\begin{spacing}{1.2}
\begin{algorithmic}[1]
    \vspace{1ex}
    \State Verify ${\tt Sig}_{\,l_r}(\bar{h}_r)$
    \State Verify that $r$ is the current round
    \State Verify that $l_r$ is the round leader
    \State Reconstruct and verify $s_r$ by Algorithm~\ref{alg:bs-valid}
    % \State Verify $\rho\left(\Sigma_r\right)$
    \For{$i=1,2,\dots,d$}
        \If{$i>1$}
            \State Verify that $\pi_{u,i-1} < \pi_{u,i}$
        \EndIf
        \State Reconstruct and Verify $e_{u_i,r}$ by Algorithm~\ref{alg:endorse-valid}
    \EndFor
    % \State Construct $\Gamma_r$ and verify ${\tt Sig}_{\,l_r}(\Gamma_r)$
    % \State Construct header body~$\Omega$ and verify ${\tt Sig}_{\,l_r}(\Omega)$
    % \State Verify $\Sigma_r$ 
\end{algorithmic}
\end{spacing}
\end{algorithm}
